---
title: "SeatGeekR"
author: "Mike Gahan"
date: "10/25/2017"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(knitr)
library(SeatGeekR)
```

## SeatgeekR

### Example

A *R* package that allows the user to scrape ticket information from the Seatgeek API

```{r}
exampleOutput <- seatgeek_extract_slug(TEAM_NAME="nebraska-cornhuskers-football")
kable(exampleOutput[, .(title, stats.average_price, stats.highest_price, stats.listing_count, stats.lowest_price)])
```

### API Keys

Before accessing the API, you must visit the SeatGeek API and create your credentials here;

https://seatgeek.com/account/develop

Seatgeek makes it pretty easy to get your credentials. Also, as of this time, Seatgeek does not really seem to have limits on their API.

### Team Names

Right now, this package has the main functionality of being able to search by team name. In the future, I hope to allow the app to search
by more. I do have a list of teamnames available for those interested.

```{r}
fpath <- system.file("Teams", "Team_Slug_Names.csv", package="SeatGeekR")
TeamNames <- fread(fpath)
kable(tail(TeamNames))
```